Signatures of Foreground Sky in Power Spectra of Redshifted Neutral Hydrogen from the Epoch of Reionization

### 2014-09-12 foreground_delay_spectrum_modeling.tex
modified FHD citation sentence a little

The data are flagged\footnote{\url{http://sourceforge.net/p/aoflagger}} for interference \citep{off12,off10}, removing 3\% of the data and averaged in time  and frequency from the raw 0.5~s, 40~kHz to 2s, 80~kHz. These data are then calibrated to a simulation of the sky containing 2420 point--like objects selected from the MWA Commissioning Survey (MWACS; Hurley-Walker et al, in prep). MWACS was compiled using observations taken with subsets of the array during the final buildout and commissioning. It has a flux density limit of 25~mJy and a declination range of -12\arcdeg to -40\arcdeg evenly covering the field of view of the observations reported here. The objects used in calibration are selected to lie inside the 5\% contour of the primary lobe of the tile power--pattern. The calibration algorithm \citep{sul12} computes complex gain solutions per channel per antenna averaged to two minute intervals. The solutions are still fairly low signal--to--noise so we iteratively project along the antenna and frequency dimensions to capture the relatively independent passband and antenna--to--antenna variation. First, we average the channel gains over all antenna to obtain a high signal--to--noise measurement of the bandpass. After applying this single passband, we do a second round of calibration and fit second and first order polynomials for amplitude and phase respectively for each antenna. This flattens any residual variation in bandpass and removes small phase slopes due to variation in cable delay. Finally, we fit for an additional phase known to be caused by reflection in 150~m length cables. %possibly could add elaboration, if I knew exactly which version of the cal was done here. doesn't really matter

@@

We show results of delay spectrum from MWA data after deconvolution along delay axis in figure~\ref{fig:fhd_data}. The principle feature is the wedge--shaped structure, the boundaries of which, marked by solid white lines, increases approximately ({\bf why exactly is it only approximate?}) linearly with light travel time corresponding to the baseline length. Note that the wedge is not filled out uniformly. Each baseline has a different orientation and resulting response to different objects in the sky. It is this variation that we are investigating.

>>>>

The data are flagged\footnote{\url{http://sourceforge.net/p/aoflagger}} for interference \citep{off12,off10}, removing 3\% of the data and averaged in time  and frequency from the raw 0.5~s, 40~kHz to 2s, 80~kHz. These data are then calibrated to a simulation of the sky containing 2420 point--like objects selected from the MWA Commissioning Survey (MWACS; Hurley-Walker et al, in prep). MWACS was compiled using observations taken with subsets of the array during the final buildout and commissioning. It has a flux density limit of 25~mJy and a declination range of -12\arcdeg to -40\arcdeg evenly covering the field of view of the observations reported here. The objects used in calibration are selected to lie inside the 5\% contour of the primary lobe of the tile power--pattern. The calibration algorithm --based on a forward modeling software by \citet{sul12}-- computes complex gain solutions per channel per antenna averaged to two minute intervals. The solutions are still fairly low signal--to--noise so we iteratively project along the antenna and frequency dimensions to capture the relatively independent passband and antenna--to--antenna variation. First, we average the channel gains over all antenna to obtain a high signal--to--noise measurement of the bandpass. After applying this single passband, we do a second round of calibration and fit second and first order polynomials for amplitude and phase respectively for each antenna. This flattens any residual variation in bandpass and removes small phase slopes due to variation in cable delay. Finally, we fit for an additional phase known to be caused by reflection in 150~m length cables. %possibly could add elaboration, if I knew exactly which version of the cal was done here. doesn't really matter

@@

We show results of delay spectrum from MWA data after deconvolution along delay axis in figure~\ref{fig:fhd_data}. The principle feature is the wedge--shaped structure, the boundaries of which, marked by solid white lines, increases linearly with light travel time corresponding to the baseline length. Note that the wedge is not filled out uniformly. Each baseline has a different orientation and resulting response to different objects in the sky. It is this variation that we are investigating.
